\documentclass[11pt]{article}
\usepackage{hyperref}
\pagestyle{empty}
\parindent 0px

\title{Text and Document Formatting}
\author{Abdulqadir Saieb}
\date{\today}

\begin{document}
\maketitle

\section{Text Formatting:}
\subsection{Font Types}
This will produce \textit{italicized} text.\\

This will produce \textbf{bold faceted} text.\\

This will produce \textsc{small caps} text.\\

This will produce \texttt{typewriter font} text.\\

This is a link to \texttt{http://website.com} (Not clickable).\\

\subsection{Clickable Link:}
Please visit my page at \href{https:/example.com}{Website}.\\

\subsection{Font Sizes:}
Please excuse my dear aunt Sally. (Normal size text.)

\vspace{1cm}
Please excuse my \begin{large}dear aunt Sally.
\end{large}

\vspace{1cm}
Please excuse my \begin{Large}dear aunt Sally.
\end{Large}

\vspace{1cm}
Please excuse my \begin{LARGE}dear aunt Sally.
\end{LARGE}


\vspace{1cm}
Please excuse my \begin{huge}dear aunt Sally.
\end{huge}

\vspace{1cm}
Please excuse my \begin{Huge}dear aunt Sally.
\end{Huge}

\vspace{1cm}
Please excuse my \begin{small}dear aunt Sally.
\end{small} 

\vspace{1cm}
Please excuse my \begin{scriptsize}dear aunt Sally.
\end{scriptsize}

\vspace{1cm}
Please excuse my \begin{tiny}dear aunt Sally.
\end{tiny}\\

\Large
Please excuse my dear aunt Sally.

\subsection{Text Indentation:}
\begin{center}
This text is centered.
\end{center}

\begin{flushleft}
This text is left-justified.
\end{flushleft}

\begin{flushright}
This text is right-justified.
\end{flushright}

%\center
%\tiny
This line is centered.\\
This line is left-justified.\\
This line is right-justified.\\


\pagebreak
\section{Document Formatting:}

\end{document}


\documentclass[11pt]{article}
\begin{document}
\section{Linear Functions}
	\subsection{Slope-Intercept Form}
	\subsection{Standard Form}
	\subsection{Point-Slope Form}
\section{Quadratic Functions}
\end{document}